Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-04 article-models-ttconstr.tex
working on extension algebras

>>>>

\begin{comment}
\section{Intensional algebras for the theory of contexts, families and terms}
In this section we investigate intensional algebras for the theory of contexts,
families and terms. These are algebras in a weak sense: the judgmental
equalities are replaced by propositional equalities and in some cases coherence
properties are added. The goal writing intensional algebras is twofold: first,
it allows for easy formalization in existing proof assistants such as \Coq;
second, we are shooting at an internal definition of internal weak 
$\infty$-groupoids.

\subsection{Intensional extension algebras}

\begin{defn}
An intensional extension algebra in context $\Gamma$ consists of
\begin{enumerate}
\item A type $C$ in context $\Gamma$
\item A type family $F:C\to\type$
\item A function $\epsilon_0:(\sm{x:C}F(x))\to C$.
\item A function $\epsilon_1:\prd{x:C}(\sm{y:F(x)}F(\epsilon_0(x,y)))\to F(x)$
\end{enumerate}
\end{defn}
\end{comment}

### 2014-06-04 article-models-ttinternal.tex
added remark about diagrams of type theory
working on extension algebras

\begin{defn}\label{defn:extension-algebras}
An \emph{extension algebra $\extalg{A}$ in context $\Gamma$} is a quadruple 
\begin{equation*}
\unfold{\extalg{A}}
\end{equation*}
consisting of 
\begin{enumerate}
\item a family $\cftalgc{\cftalg{A}}$ over context $\Gamma$, 
\item a family $\cftalgf{\cftalg{A}}$ over the context
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$,
\item a morphism $\cftctxext[\cftalg{A}]$ from $\ctxext{\cftalgc{\cftalg{A}}}{
\cftalgf{\cftalg{A}}}$ to $\cftalgc{\cftalg{A}}$ in context
$\Gamma$
\item a morphism $\cftfamext[\cftalg{A}]$ from 
$\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}$ 
to $\cftalgf{\cftalg{A}}$ in context
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$,
\end{enumerate}
satisfying the judgmental equalities of
\autoref{eq:extalg-eq1,eq:extalg-eq2}.

@@

\begin{thm}
Suppose that $\extalg{A}$ is an extension algebra in context
$\Gamma$. Then 
\begin{equation*}
\cftalg{F_A}\defeq(\cftalgf{\cftalg{A}},\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}},\cftfamext,\jcomp{}{\cftctxext}{\cftfamext})
\end{equation*}
is an extension algebra in context $\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

@@

\begin{defn}
An \emph{extension homomorphism $\exthom{f}$ from $\extalg{A}$ to
$\extalg{B}$ in context $\Gamma$} is a pair $\unfold{\exthom{f}}$ consisting of
\begin{align*}
\jhom*{\Gamma}{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{B}}}{\cfthomc{\cfthom{f}}}
  \\
\jfhom*{\Gamma}{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{B}}}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{B}}}{\cfthomf{\cfthom{f}}}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:extalg-hom1}
\begin{tikzcd}
\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
  \ar{r}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  \ar{d}[swap]{\cftctxext[\cftalg{A}]}
& \ctxext{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}
  \ar{d}{\cftctxext[\cftalg{B}]}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}[swap]{\cfthomc{\cfthom{f}}}
& \cftalgc{\cftalg{A}}
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:extalg-hom2}
\begin{tikzcd}[column sep=huge]
\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
  \ar{r}{\jvcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}}}
  \ar{d}[swap]{\cftfamext[\cftalg{A}]}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\ctxext{\cftalgf{\cftalg{B}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
  \ar{d}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftfamext[\cftalg{B}]}}
  \\
\cftalgf{\cftalg{A}}
  \ar{r}[swap]{\cfthomf{\cfthom{f}}}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}

\begin{rmk}
To see that the upper morphism in the diagram of \autoref{eq:extalg-hom2} has
indeed the indicated codomain provided that the diagram of \autoref{eq:extalg-hom1}
commutes judgmentally, note that we have the judgmental equalities
\begin{align*}
\jcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cfthomc{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
& \jdeq 
  \jcomp{}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}
  \tag{by \autoref{lem:composition-threesome}}
  \\
& \jdeq
  \jcomp{}{\jcomp{}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}{\cftctxext[\cftalg{B}]}}{\cftalgf{\cftalg{B}}}
  \tag{by \autoref{lem:jcomp-jcomp}}
  \\
& \jdeq
  \jcomp{}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomc{\cfthom{f}}}}{\cftalgf{\cftalg{B}}}
  \tag{by \autoref{eq:extalg-hom1}}
  \\
& \jdeq
  \jcomp{}{\cftctxext[\cftalg{A}]}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}}.
  \tag{by \autoref{lem:jcomp-jcomp}}
\end{align*}
and we indeed have the morphism $\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}$ from 
$\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}$ to $\jcomp{}{\cftctxext[\cftalg{A}]}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}}$.
\end{rmk}

@@

\begin{proof}
We have to verify that the diagrams in \autoref{eq:extalg-hom1,eq:extalg-hom2}
commute for $\cfthom{F_f}$. Unfolding the ingredients of \autoref{eq:extalg-hom1}
for $\cfthom{F_f}$ gives us quite directly \autoref{eq:extalg-hom2}. The
diagram in \autoref{eq:extalg-hom2} for $\cfthom{F_f}$ is judgmentally equal
to the pullback of everything in the diagram in \autoref{eq:extalg-hom2} for
$\cfthom{f}$ by $\epsilon_0$, and therefore it commutes too.
\end{proof}

@@

A term-algebra $\cftalg{A}$ in context $\Gamma$ is going to be a septuple
\begin{equation*}
(\cftalgc{\cftalg{A}},\cftalgf{\cftalg{A}},\cftalgt{\cftalg{A}},
\cftctxext[\cftalg{A}],\cftfamext[\cftalg{A}],\cftempc{\cftalg{A}},
\cftempf{\cftalg{A}})
\end{equation*}
for which 
the quadruple $\unfold{\extalg{A}}$ is an extension algebra in context 
$\Gamma$, the quintuple $\unfold{\empalg{A}}$ is an empty-object algebra in context
$\Gamma$, satisfying additional judgmental equalities expressing the 
compatibility of $\cftctxext[\cftalg{A}]$ and $\cftfamext[\cftalg{A}]$ with 
$\cftempc{\cftalg{A}}$ and $\cftempf{\cftalg{A}}$.
There will be five such judgmental equalities. Four of them will express that
extension acts as the identity term when applied to the empty object in one of
its arguments. The other expresses that family extension restricted to
families above the empty object is the same as context extension. To be able
to state these, we need to know that $\unfold{\empalg{A}}$ is an empty-object
algebra. In the following, we verify step-by-step that we can indeed make the
suggested requirements.
\begin{enumerate}
\item The type of $\subst{\cftempc{\cftalg{A}}}{\cftctxext[\cftalg{A}]}$ is
$\subst
  { \cftempc{\cftalg{A}}
    }
  { \ctxwk
      {\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      {\cftalgc{\cftalg{A}}}
    }$.
We have the judgmental equalities
\begin{align*}
\subst
  { \cftempc{\cftalg{A}}
    }
  { \ctxwk
      {\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      {\cftalgc{\cftalg{A}}}
    }
& \jdeq
  \subst
    { \cftempc{\cftalg{A}}
      }
    { \ctxwk
        { \cftalgf{\cftalg{A}}
          }
        { {\cftalgc{\cftalg{A}}}
          {\cftalgc{\cftalg{A}}}
          }
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \ctxwk
    { \subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
      }
    { \subst{\cftempc{\cftalg{A}}}{\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
      }
  \tag{by \autoref{comp-sw-f}}
\end{align*}
\end{enumerate}

>>>>

\begin{defn}\label{defn:extension-algebras}
We define the judgment
\begin{equation*}
\jextalg{\Gamma}{A}
\end{equation*}
asserting that $\extalg{A}$ is an \emph{extension algebra in context $\Gamma$}
to be the conjunction of the following six judmgents:
\begin{align*}
\jextalgctx*{\Gamma}{A}
  \\
\jextalgfam*{\Gamma}{A}
  \\
\jextalgctxext*{\Gamma}{A}
  \\
\jextalgfamext*{\Gamma}{A}
  \\
\jhomeq*
  { \Gamma}
  { {\cftalgc{\cftalg{A}}}
    { {\cftalgf{\cftalg{A}}}
      {\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
      }
    }
  { \cftalgc{\cftalg{A}}}
  { \jcomp{}
      { \jvcomp{}
          {\cftctxext[\cftalg{A}]}
          {\idtm{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}}
        }
      { \cftctxext[\cftalg{A}]}
    }
  { \jcomp{}
      { \jvcomp{}
          {\idtm{\cftalgc{\cftalg{A}}}}
          {\cftfamext[\cftalg{A}]}
        }
      { \cftctxext[\cftalg{A}]}
    }
  \\
\jhomeq*
  { {\Gamma}{\cftalgc{\cftalg{A}}}}
  { { \cftalgf{\cftalg{A}}}
    { { \jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
      { \jcomp{}
          {\cftctxext[\cftalg{A}]}
          {{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
        }
      }
    }
  { \cftalgf{\cftalg{A}}}
  { \jcomp{}
      { \cftfamext[\cftalg{A}]}
      { \jvcomp{}
          {\cftfamext[\cftalg{A}]}
          {\idtm{\jcomp{}{\cftfamext[\cftalg{A}]}{{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}}}}
    }
  { \jcomp{}
      { \cftfamext[\cftalg{A}]}
      { \jvcomp{}
          {\idtm{\cftalgf{\cftalg{A}}}}
          {\jcomp{}{\cftctxext[\cftalg{A}]}{\cftfamext[\cftalg{A}]}}
        }
    }
\end{align*}
In other words, an extension algebra $\extalg{A}$ in context $\Gamma$
is a quadruple $\unfold{\extalg{A}}$ 
satisfying the judgmental equalities of
\autoref{eq:extalg-eq1,eq:extalg-eq2}. Extension algebras are judgmentally
equal if they are componentwise judgmentally equal.

@@

\begin{thm}\label{thm:extalg-fam}
Suppose that $\extalg{A}$ is an extension algebra in context
$\Gamma$. Then 
\begin{equation*}
\cftalg{F_A}\defeq(\cftalgf{\cftalg{A}},\jcomp{}{\cftctxext}{\cftalgf{\cftalg{A}}},\cftfamext,\jcomp{}{\cftctxext}{\cftfamext})
\end{equation*}
is an extension algebra in context $\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$.
\end{thm}

@@

\begin{cor}
Let $\extalg{A}$ be an extension algebra in context $\Gamma$. Then
$\extalg{F_{F_A}}$ and $\jcomp{}{\cftctxext[\extalg{A}]}{\extalg{F_A}}$ are
judgmentally equal extension algebras in context $\ctxext{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}$.
\end{cor}

\begin{defn}
An \emph{extension homomorphism $\exthom{f}$ from $\extalg{A}$ to
$\extalg{B}$ in context $\Gamma$} is a pair $\unfold{\exthom{f}}$ consisting of
\begin{align*}
\jhom*{\Gamma}{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{B}}}{\cfthomc{\cfthom{f}}}
  \\
\jfhom*{\Gamma}{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{B}}}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{B}}}{\cfthomf{\cfthom{f}}}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:exthom1}
\begin{tikzcd}
\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
  \ar{r}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  \ar{d}[swap]{\cftctxext[\cftalg{A}]}
& \ctxext{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}
  \ar{d}{\cftctxext[\cftalg{B}]}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}[swap]{\cfthomc{\cfthom{f}}}
& \cftalgc{\cftalg{A}}
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:exthom2}
\begin{tikzcd}[column sep=huge]
\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}}
  \ar{r}{\jvcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}}}
  \ar{d}[swap]{\cftfamext[\cftalg{A}]}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\ctxext{\cftalgf{\cftalg{B}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
  \ar{d}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftfamext[\cftalg{B}]}}
  \\
\cftalgf{\cftalg{A}}
  \ar{r}[swap]{\cfthomf{\cfthom{f}}}
& \jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}

\begin{rmk}
To see that the upper morphism in the diagram of \autoref{eq:exthom2} has
indeed the indicated codomain provided that the diagram of \autoref{eq:exthom1}
commutes judgmentally, note that we have the judgmental equalities
\begin{align*}
\jcomp{}{\cfthomf{\cfthom{f}}}{\jcomp{}{\cfthomc{\cfthom{f}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}}
& \jdeq 
  \jcomp{}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}{\jcomp{}{\cftctxext[\cftalg{B}]}{\cftalgf{\cftalg{B}}}}
  \tag{by \autoref{lem:composition-threesome}}
  \\
& \jdeq
  \jcomp{}{\jcomp{}{\jvcomp{}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}{\cftctxext[\cftalg{B}]}}{\cftalgf{\cftalg{B}}}
  \tag{by \autoref{lem:jcomp-jcomp}}
  \\
& \jdeq
  \jcomp{}{\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomc{\cfthom{f}}}}{\cftalgf{\cftalg{B}}}
  \tag{by \autoref{eq:exthom1}}
  \\
& \jdeq
  \jcomp{}{\cftctxext[\cftalg{A}]}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}}.
  \tag{by \autoref{lem:jcomp-jcomp}}
\end{align*}
and we indeed have the morphism $\jcomp{}{\cftctxext[\cftalg{A}]}{\cfthomf{\cfthom{f}}}$ from 
$\jcomp{}{\cftctxext[\cftalg{A}]}{\cftalgf{\cftalg{A}}}$ to $\jcomp{}{\cftctxext[\cftalg{A}]}{\jcomp{}{\cfthomc{\cfthom{f}}}{\cftalgf{\cftalg{B}}}}$.
\end{rmk}

@@

\begin{proof}
We have to verify that the diagrams in \autoref{eq:exthom1,eq:exthom2}
commute for $\cfthom{F_f}$. Unfolding the ingredients of \autoref{eq:exthom1}
for $\cfthom{F_f}$ gives us quite directly \autoref{eq:exthom2}. The
diagram in \autoref{eq:exthom2} for $\cfthom{F_f}$ is judgmentally equal
to the pullback of everything in the diagram in \autoref{eq:exthom2} for
$\cfthom{f}$ by $\epsilon_0$, and therefore it commutes too.
\end{proof}

\begin{defn}
Let $\exthom{f}$ and $\exthom{g}$ be extension homomorphisms from
$\extalg{A}$ to $\extalg{B}$ and from $\extalg{B}$ to $\extalg{C}$, respectively.
We define the composition
\begin{equation*}
\exthomcomp{\exthom{f}}{\exthom{g}}
  \defeq
  \unfold{\exthomcomp{\exthom{f}}{\exthom{g}}}.
\end{equation*}
In other words, extension homomorphisms are composed by taking the outer rectangle
in the diagram
\begin{equation*}
\begin{tikzcd}
\extalgf{\extalg{A}} 
  \ar[fib]{d}
  \ar{r}{\exthomf{\exthom{f}}}
& \extalgf{\extalg{B}} 
  \ar[fib]{d}
  \ar{r}{\exthomf{\exthom{g}}}
& \extalgf{\extalg{C}}
  \ar[fib]{d}
  \\
\extalgc{\extalg{A}}
  \ar{r}{\exthomc{\exthom{f}}}
& \extalgc{\extalg{B}}
  \ar{r}{\exthomc{\exthom{g}}}
& \extalgc{\extalg{C}}
\end{tikzcd}
\end{equation*}
\end{defn}

\begin{rmk}
It follows from \autoref{lem:jcomp-jcomp,lem:jfcomp-jfcomp} that composition
of extension homomorphisms is associative.
\end{rmk}

\begin{thm}
Let $\exthom{f}$ and $\exthom{g}$ be extension homomorphisms from
$\extalg{A}$ to $\extalg{B}$ and from $\extalg{B}$ to $\extalg{C}$, respectively.
Then $\exthomcomp{\exthom{f}}{\exthom{g}}$ is an extension homomorphism from
$\extalg{A}$ to $\extalg{C}$. 
\end{thm}

\begin{proof}
Both judgmental equalities are applications of the interchange law for composition,
\autoref{lem:composition-interchange}. 
\end{proof}

The following theorem explains how context extension can be seen as an extension
homomorphism. Note that in combination with \autoref{thm:extalg-fam}, this also
explains how family extension can be seen as an extension homomorphism.

\begin{thm}
Let $\extalg{A}$ be an extension algebra in context $\Gamma$. Then
\begin{align*}
& ( \ctxext{\extalgc{\extalg{A}}}{\extalgf{\extalg{A}}},
    \jcomp{}{\cftctxext}{\extalgf{\extalg{A}}},
    \jvcomp{}{\ctxwk{\extalgf{\extalg{A}}}{\idtm{\extalgc{\extalg{A}}}}}{\cftfamext},
    \jcomp{}{\cftctxext}{\cftfamext}
    )
\intertext{and}
& ( \ctxext{\extalgc{\extalg{A}}}{\extalgf{\extalg{A}}},
    \jcomp{}{\cftctxext}{\extalgf{\extalg{A}}},
    \jvcomp{}{\cftctxext}{\idtm{\jcomp{}{\cftctxext}{\extalgf{\extalg{A}}}}},
    \jcomp{}{\cftctxext}{\cftfamext}
    )
\end{align*}
are extension algebras in context $\Gamma$ and
\begin{equation*}
\boldsymbol{\cftctxext}\defeq ( \cftctxext,
  \idtm{\jcomp{}{\cftctxext}{\extalgf{\extalg{A}}}}
  )
\end{equation*}
is an extension homomorphism from both of them to $\extalg{A}$. 
\end{thm}

@@

A term-algebra $\cftalg{A}$ in context $\Gamma$ is going to be a septuple
\begin{equation*}
(\cftalgc{\cftalg{A}},\cftalgf{\cftalg{A}},\cftalgt{\cftalg{A}},
\cftctxext[\cftalg{A}],\cftfamext[\cftalg{A}],\cftempc{\cftalg{A}},
\cftempf{\cftalg{A}})
\end{equation*}
for which 
the quadruple $\unfold{\extalg{A}}$ is an extension algebra in context 
$\Gamma$, the quintuple $\unfold{\empalg{A}}$ is an empty-object algebra in context
$\Gamma$, satisfying additional judgmental equalities expressing the 
compatibility of $\cftctxext[\cftalg{A}]$ and $\cftfamext[\cftalg{A}]$ with 
$\cftempc{\cftalg{A}}$ and $\cftempf{\cftalg{A}}$.
There will be five such judgmental equalities. Four of them will express that
extension acts as the identity term when applied to the empty object in one of
its arguments. The other expresses that family extension restricted to
families above the empty object is the same as context extension. To be able
to state these, we need to know that $\unfold{\empalg{A}}$ is an empty-object
algebra. In the following, we verify step-by-step that we can indeed make the
suggested requirements.
\begin{enumerate}
\item The type of $\subst{\cftempc{\cftalg{A}}}{\cftctxext[\cftalg{A}]}$ is
$\subst
  { \cftempc{\cftalg{A}}
    }
  { \ctxwk
      {\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      {\cftalgc{\cftalg{A}}}
    }$.
We have the judgmental equalities
\begin{align*}
\subst
  { \cftempc{\cftalg{A}}
    }
  { \ctxwk
      {\ctxext{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      {\cftalgc{\cftalg{A}}}
    }
& \jdeq
  \subst
    { \cftempc{\cftalg{A}}
      }
    { \ctxwk
        { \cftalgf{\cftalg{A}}
          }
        { {\cftalgc{\cftalg{A}}}
          {\cftalgc{\cftalg{A}}}
          }
      }
  \tag{by \autoref{comp-ew-f}}
  \\
& \jdeq
  \ctxwk
    { \subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
      }
    { \subst{\cftempc{\cftalg{A}}}{\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}
      }
  \tag{by \autoref{comp-sw-f}}
  \\
& \jdeq
  \ctxwk
    { \subst{\cftempc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}
      }
    { A
      }
  \tag{by \autoref{cancellation-ws-f}}
  \\
& \jdeq
  \ctxwk{A}{A}
  \tag{by \autoref{empalg-eq2}}
\end{align*}
Thus, we require that
\begin{equation}
\jtermeq{{\Gamma}{\cftalgc{\cftalg{A}}}}{\ctxwk{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{A}}}}{\subst{\cftempc{\cftalg{A}}}{\cftctxext[\cftalg{A}]}}{\idtm{\cftalgc{\cftalg{A}}}}
  \label{extempalg-eq1}
\end{equation}
\end{enumerate}
